Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-26 manuscript/manuscript.tex
Minor text modification

The comparison between the numerical results and the analytical solution could be
naively compared on a single computation point due to the rotation symmetry of the
spherical shell.
But the numerical results may adopt different values depending on the relative location
between the computation point and the tesseroid, thus is not wise to carry out the
comparison on a single point.
Instead, we propose four computation grids detailed on Table~\ref{tab:grids}: a Pole and
an Equator grids, and a Global and Satellite grids.
The former ones are regional scale grids located on the outer surface of the spherical
shell, while the latter are global scale grids located at zero height (Global) and at
the mean orbital height of the gravimetric satellite missions (Satellite).
We define these grids in the spirit of spanning a broad scenario of gravitational field
computations and ensure an acceptable accuracy on each one of them.
The comparison will be carried out by computing the maximum absolute difference between
the analytical solution and the numerical result on each point of the computation grid.

>>>>

The comparison between the numerical results and the analytical solution could be
naively compared on a single computation point due to the rotation symmetry of the
spherical shell.
But the numerical results may adopt different values depending on the relative location
between the computation point and the tesseroid, thus is not wise to carry out the
comparison on a single point.
Instead, we propose four computation grids detailed on Table~\ref{tab:grids}: a Pole and
an Equator grids, and a Global and Satellite grids.
The former ones are regional scale grids located on the outer surface of the spherical
shell, while the latter are global scale grids located at zero height (Global) and at
the mean orbital height of the gravimetric satellite missions (Satellite).
These grids are defined in the spirit of spanning a broad scenario of gravitational
field computations and ensure an acceptable accuracy on each one of them.
The comparison will be carried out by computing the maximum absolute difference between
the analytical solution and the numerical result on each point of the computation grid.
